---
title: "Tablet app metadata"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminaries

Note that the `results = 'hide'` flag is set in the chunks below. This avoids writing sensitive data to reports that might be pushed to public/open access directories.

Data were stored in .xml files on Adolph lab server within participant-specific folders. These are now copied to a local set of directories stored in a shared Box folder. The path on Rick's computer is:

```{r, echo = FALSE}
data_path <- "~/Box\ Sync/play-demog-data-from-app-pilots/data/xml"
```

`r data_path`

## Opening a sample XML file from a sample participant

```{r packages, echo=TRUE, results='hide'}

# Install package to work with XML files if needed
# install.packages("XML")

# Then load into current space
library("XML")

xml_list <- list.files(data_path, pattern = "\\.xml$", full.names = TRUE)

participant_index <- 1

# Surround in () to print variable
(xml_file <- xmlParse(file = xml_list[[participant_index]]))
xml_top <- xmlRoot(xml_file) # grabs top node
```

It looks like we have the following overall structure:

```
<Combined_Questionnaires>
  <phone_questionnaire>
    Infant characteristics
    Mom characteristics
    Family characteristics
  <home_questionnaire>
    Locomotor milestones
    MacArthur
    Media Use
    Rothbart ECBQ
    Home environment
```

I suspect that we will want separate data files for each of the questionnaire measures and a single file with the demographic data collected during the phone questionnaire.

### Phone questionnaire data

```{r phone-quest, echo=TRUE, results='hide'}
(xml_top[[5]]) # gives data from <phone_questionnaire>
```

### Home questionnaire data

```{r home-quest, echo=TRUE, results='hide'}
(xml_top[[6]]) # gives <home_questionnaire data>

xml_top[[6]][[2]] # gives sex and test date
xml_top[[6]][[3]] # gives child exact age and agegroup
xml_top[[6]][[4]] # gives date of child's 6 mo birthday, 5:24 generate similar
                 # dates up to 24 mos
xml_top[[6]][[23]] # footwear data

xml_top[[6]][[25]] # loc_milestones_walk
xml_top[[6]][[26]] # walk_onset_mos

xml_top[[6]][[28]] # loc_milestones_crawl
xml_top[[6]][[29]] # crawl_onset_mos

xml_top[[6]][[32]] # macarthur_2_e

xml_top[[6]][[33]] # media_use_p1
xml_top[[6]][[34]] # media_use_p2
xml_top[[6]][[35]] # media_use_p3
xml_top[[6]][[36]] # media_use_p4

xml_top[[6]][[37]] # Rothbart ECBQ

xml_top[[6]][[38]] # HOME environment
```